TersectBrowser+ : A single browser for in-depth introgression analysis of re-sequenced genome datesets

### 2025-04-26 Article/Article.tex
Structure Update

\title[Short Article Title]{TersectBrowser+ : A single browser for in-depth introgression analysis of resequenced genome datsaets}

@@

@@

@@

The field of tomato genomics has continued to evolve rapidly, with a growing emphasis on mapping introgressions — segments of DNA from wild tomato species that have been incorporated into cultivated lines. Foundational work such as that by Aflitos et al. \cite{RN7} , which sequenced 84 tomato accessions and wild relatives, exposed severe genetic bottlenecks in cultivated tomatoes and laid the groundwork for modern introgression analysis.

@@

\section{This is an example for first level head}\label{sec3}

\subsection{This is an example for second level head - subsection head}\label{subsec2}

\subsubsection{This is an example for third level head - subsubsection head}\label{subsubsec2}

\paragraph{This is an example for fourth level head - paragraph head}

\section{Conclusion}

Some Conclusions here.

@@

\begin{appendices}

\section{Section title of first appendix}\label{sec11}

\subsection{Subsection title of first appendix}\label{subsec4}

\section{Example of another appendix section}\label{sec13}%

\end{appendices}

@@

\section{Competing interests}

\section{Author contributions statement}

\section{Acknowledgments}

\bibliography{examplerefs}

\begin{thebibliography}{10}
\bibitem{bahdanau2014neural}
Dzmitry Bahdanau, Kyunghyun Cho, and Yoshua Bengio.
\newblock Neural machine translation by jointly learning to align and
  translate.
\newblock {\em arXiv preprint arXiv:1409.0473}, 2014.
\end{thebibliography}

>>>>

\title[Short Article Title]{TersectBrowser+ : A single browser for in-depth introgression analysis of re-sequenced genome datesets}

@@

% Variant comparison important, tools are slow, what Tersect does. Tersect produced because tools slow. We modify Tersect creating Tersect+ to bringing additional functionality to aid the investigation of cultivar introgressions for biologists.

@@

% # Intro / Current Situation & Problem & Tersect Solution
% Large-scale resequencing projects enable comparative genomic studies to identify key variants and structures like haplotypes or introgressions. studies rely on set theoretical operations, but current tools (e.g., BEDOPS, BCFtools, BEDTools) are limited in query complexity and speed. Tersect, using its own query language and fast execution through bitmap indices, enabling complex, real-time genome queries. This will become: a part on slowness 'As shown in [ref = Tom Fady paper] tools slow'. Then add something on functionality of these tools EITHER 'slow tools have functionality' or 'tools do not have functionality'.  Then 'Tersect+ provides functionality.

@@

The field of tomato genomics has continued to evolve rapidly, with a growing emphasis on mapping introgressions — segments of DNA from wild tomato species that have been incorporated into cultivated lines. Foundational work such as that by Aflitos et al. (2014) , which sequenced 84 tomato accessions and wild relatives, exposed severe genetic bottlenecks in cultivated tomatoes and laid the groundwork for modern introgression analysis.

@@

\section{Tersect Browser+}

% # Built based on Tersect Browswer... About Tersect About Tersect+- unified database, indexes and tracks and how speed is achieved. 
% Builds a unified allele database from VCF files, using bitmap indexing to track presence/absence of variants. The system links variant positions to bitmap indices, allowing efficient region-specific searches and genome comparisons via compressed, sparse data structures. Indexing is fast and optimized for read-heavy workflows. While updating is less efficient, batch additions mitigate this. A custom parser converts set-based queries into abstract syntax trees (ASTs), which are then optimized and reused across queries for speed.  We summarize here the functionality. Probably in the following structure. Browser; Models; Search; and Barcodes and Introgressions [if we get there.] We do this with a paragraph on each. We write similarly to the Fady and Tom email. We could do it in two parts:  Browser and Gene Model and Search and Barcodes including introgression search, we do that. The structure in paragraphs will be:

\section{Features}

% Browser  - all these will be kept short paragraphs.
% Gene Models
% Search 
% Barcodes
% [Introgression]

\section{Funding}

%\section{This is an example for first level head}\label{sec3}

% \subsection{This is an example for second level head - subsection head}\label{subsec2}

% \subsubsection{This is an example for third level head - subsubsection head}\label{subsubsec2}

% \paragraph{This is an example for fourth level head - paragraph head}

% \section{Conclusion}

% Some Conclusions here.

@@

@@

% \section{Competing interests}

% \section{Author contributions statement}

% \section{Acknowledgments}

\bibliographystyle{plain}
\bibliography{Article/article_ref}
